Variation on a Variational Principle

### 2020-09-13 draft1.tex
middle of proving thm; detour to do prop about +- deform theta stuff.

@@

%This command stops the Math Review numbers appearing in the references! 
\AtBeginDocument{
   \def\MR#1{}
}
\newcommand{\Sp}{\rm{S}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\HH}{\mathbb{H}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\bfloor}[1]{\left\lfloor #1\right\rfloor}
\renewcommand{\P}{\mathcal P}
\newcommand{\A}{\mathcal A}
\newcommand{\W}{\mathcal W}
\newcommand{\vol}{{\rm vol}}
\newcommand{\cut}{{\backslash \backslash}}
\newcommand{\bdy}{\partial}
\newcommand{\voct}{{v_{\rm oct}}}
\newcommand{\vtet}{{v_{\rm tet}}}
\renewcommand{\L}{\mathcal L}
\newcommand{\cp}{\mathcal{C}}
\newcommand{\toF}{{\overset{F}{\longrightarrow}}}
\newcommand{\K}{\upkappa}

@@

\newcommand{\del}{\partial}
\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
\newcommand{\vphi}{\varphi}
\newcommand{\llong}{{\text{long}}}
\newcommand{\Span}{{\text{span}}}
\newcommand{\Pol}{{\text{Pol}}}

@@

Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in $\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic. In this paper we investigate if this statement holds for links in the thickened torus i.e. if $L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the thickened torus. In this chapter we find many families of hyperbolic links in the thickened torus which remain hyperbolic after augmentation.

 \begin{figure}
 \centering  
 \begin{tabular}{cc}
 \includegraphics [height=4cm]{augmentation1}&
  \includegraphics [height=4cm]{augmentation2}\\
  (a)&(b)
  \end{tabular}
 \caption{The left shows a pretzel knot before augmentation and the right shows after augmentation}
 \label{fig:augmentationS3}
 \end{figure}

@@

\begin{prop}\label{thm:torihedraldecomposition}
Let $L$ be an augmented link in $T^2 \times I$. Let $G(L)$ be a diagram of the link on $T^2 \times \{0\}$. There is a decomposition of the complement, $(T^2 \times I) - L$ into two isomorphic ideal torihedra.
\end{prop}

\textit{Proof}. We will begin by assuming that there are no half twists and then arrange the link diagram of $L$ in the following way: first place the added circle components (augmentation) perpendicular to the projection plane, $T^2 \times \{0\}$ leaving the remaining part of the link parallel to the projection plane. 
We now place a crossing edge on each crossing of the link so that for each crossing edge, one end of the edge lies on a bottom strand while the other end lies on a top strand as in Figure \ref{fig:crossingArc} left.

@@

\indent We repeat the steps for the bottom half of $T^2 \times I$, $T^2 \times
[-1,0)$. Then we get two isomorphic torihedra. The graph of each will come from
crossing edges and, edges of the disk. Now, if there are half twists we will
decompose the complement of the link the same way as if there are no half twists
and we will identify the two bow-ties as in Figure \ref{fig:falGluings}. Finally
we obtain the complement of the link by gluing the two torihedra with the gluing
information given by identifying crossing edges and triangles of the bow-tie. We
glue the faces of the torihedra which do not correspond to a bow-tie with a
$\pi/n$ twist where $n$ is the number of sides of each face as in Figure
\ref{fig:top-bottom} clockwise or counterclockwise. \qed

@@

\begin{remark}\label{cor:triangulation}
The faces of one torihedron which do not correspond to a bow-tie glue to a
corresponding face of the second torihedron to form bipyramids. One can add
stellating edges, edges which have vertices corresponding to the different
components of the Hopf link that cuts through the center of the face to
decompose the bipyramids into tetrahedra. This process is called {\it
stellation}. Stellating all the bipyramids of the decomposition obtained from
Proposition \ref{thm:torihedraldecomposition} we obtained a triangulation of the
complement of $L$ which is made up of {\it horizontal} edges (edges from the
graph of the torihedra), {\it vertical} edges (edges from coning vertices of the
the graph of the torihedra) and stellating edges.  \end{remark}

{\it Proof.}  Using the decomposition from Proposition
\ref{thm:torihedraldecomposition} we can add a stellation edge whose end points
are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2
\times I$ which do not come from the augmentation disks like in \cite{CKP2}.
Since each face of the top torihedron gets glued to the bottom torihedron, we
obtain bipyramids, and the stellation edge will decompose the bipyramids into
tetrahedra. Then the link of the vertex  $T^2 \times \{1\}$ or $T^2 \times
\{-1\}$ is the graph of the torihedron $T^2 \times [0,1)$ or $T^2 \times (-1,0]$
respectively. \qed

@@

View the Euclidean plane as the boundary of the upper-half space.
Then $\Pol_f$ subtends an ideal hyperbolic pyramid $P_f$.

@@

For a hyperbolic link $K$ in $T^2 \times I$, we produce sufficient conditions on augmentations such that the resulting link obtained from augmenting $K$ is hyperbolic. The idea is to start with a graph from the torihedral decomposition of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges \cite{CKP2}. Then by results of \cite{BandS} there exist a corresponding right-angled circle pattern. We then consider the augmented link $L$ and its torihedral decomposition from Proposition \ref{thm:torihedraldecomposition} with a corresponding ``degenerate" circle pattern. We deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition of $(T^2 \times I)-L$ with angles of the torihedra in our torihedral decomposition. Which we can further decompose into tetrahedra with angles satisfying conditions of an angle structure.

@@

\begin{define}
A \emph{base-angled ideal pyramid}
is a pyramid whose base is an $n$-gon, $n \geq 3$,
and each boundary edge $e_i$ of the base face is assigned a dihedral angle $\alpha_i$
such that for adjacent edges, $\alpha_i + \alpha_{i+1} < \pi$.
The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
is automatically assigned the dihedral angle $\pi - \alpha_i - \alpha_{i+1}$.
\end{define}

Clearly, the dihedral angles of an ideal hyperbolic pyramid
make it a base-angled ideal pyramid.
(TODO probably vice-versa?)

@@

{\it Proof.} See Figure \ref{TODO}

@@

\begin{define}
Given a face $f$ of the original link diagram the \emph{augmentation sequence} of $f$, denoted $\sigma_f$ is a sequence of symbols $0, L, R$ indexed by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the $v$-th element is
\[
\sigma_f^v = 
\begin{cases}
0 \text{ if $v$ is not augmented} \\
L \text{ if $v$ is left-augmented} \\
R \text{ if $v$ is right-augmented}
\end{cases}
\]
\end{define}

@@

{\it Proof.}

Part 1:

by ckp the original link can be decomposed into torihedra with projection graph as torihedra graph with pi/2 edges and this gives circle pattern by bobenko-springborn

Part 2: Our torihedral decomposition has graph and on augmentation we will give 0 and pi angles. Next we add another edge and give blah angle (we have three cases)
do three cases with pictures

@@

>>>>

\newcommand{\thmref}[1]{Theorem \ref{#1}}
\newcommand{\prpref}[1]{Proposition \ref{#1}}

@@

%This command stops the Math Review numbers appearing in the references! 
\AtBeginDocument{
   \def\MR#1{}
}
\newcommand{\Sp}{{\rm{S}}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\HH}{\mathbb{H}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\bfloor}[1]{\left\lfloor #1\right\rfloor}
\renewcommand{\P}{\mathcal P}
\newcommand{\A}{\mathcal A}
\newcommand{\W}{\mathcal W}
\newcommand{\vol}{{\rm vol}}
\newcommand{\cut}{{\backslash \backslash}}
\newcommand{\bdy}{\partial}
\newcommand{\voct}{{v_{\rm oct}}}
\newcommand{\vtet}{{v_{\rm tet}}}
\renewcommand{\L}{\mathcal L}
\newcommand{\cp}{\mathcal{C}}
\newcommand{\toF}{{\overset{F}{\longrightarrow}}}
\newcommand{\K}{\upkappa}

@@

\newcommand{\del}{\partial}
\newcommand{\ddd}[1]{{\frac{\del}{\del #1}}}
\newcommand{\vphi}{\varphi}
\newcommand{\llong}{{\text{long}}}
\newcommand{\Span}{{\text{span}}}
\newcommand{\Pol}{{\text{Pol}}}
\newcommand{\toruscomp}[1]{{\torus \times I - #1}}

@@

Adams showed in \cite{CA} that given a hyperbolic alternating link $K$ in $\Sp^3$ the link $L$ obtained by augmentation $K$ is hyperbolic. In this paper we investigate if this statement holds for links in the thickened torus i.e. if $L$ is a link obtained from augmenting a hyperbolic alternating link $K$ in the thickened torus. In this chapter we find many families of hyperbolic links in the thickened torus which remain hyperbolic after augmentation. 
 \begin{figure}
 \centering  
 \begin{tabular}{cc}
 \includegraphics [height=4cm]{augmentation1}&
  \includegraphics [height=4cm]{augmentation2}\\
  (a)&(b)
  \end{tabular}
 \caption{The left shows a pretzel knot before augmentation and the right shows after augmentation}
 \label{fig:augmentationS3}
 \end{figure}

@@

\begin{prop}\label{p:tori_decomp}
Let $L$ be an augmented link in $T^2 \times I$.
%Let $G(L)$ be a diagram of the link on $T^2 \times \{0\}$.
There is a decomposition of the complement,
$(T^2 \times I) - L$ into two isomorphic ideal torihedra.
\end{prop}

\begin{proof}
We will begin by assuming that there are no half twists and then
arrange the link diagram of $L$ in the following way: first place the added
circle components (augmentation) perpendicular to the projection plane, $T^2
\times \{0\}$ leaving the remaining part of the link parallel to the projection
plane.  We now place a crossing edge on each crossing of the link so that for
each crossing edge, one end of the edge lies on a bottom strand while the other
end lies on a top strand as in Figure \ref{fig:crossingArc} left.

@@

\indent We repeat the steps for the bottom half of $T^2 \times I$, $T^2 \times
[-1,0)$. Then we get two isomorphic torihedra. The graph of each will come from
crossing edges and, edges of the disk. Now, if there are half twists we will
decompose the complement of the link the same way as if there are no half twists
and we will identify the two bow-ties as in Figure \ref{fig:falGluings}. Finally
we obtain the complement of the link by gluing the two torihedra with the gluing
information given by identifying crossing edges and triangles of the bow-tie. We
glue the faces of the torihedra which do not correspond to a bow-tie with a
$\pi/n$ twist where $n$ is the number of sides of each face as in Figure
\ref{fig:top-bottom} clockwise or counterclockwise.

For future reference, we will denote the graph for the top and bottom
torihedra by $\Gamma_T(L)$ and $\Gamma_B(L)$, respectively.
\end{proof}

@@

\begin{remark}\label{cor:triangulation}
The faces of one torihedron which do not correspond to a bow-tie glue to a
corresponding face of the second torihedron to form bipyramids. One can add
stellating edges, edges which have vertices corresponding to the different
components of the Hopf link that cuts through the center of the face to
decompose the bipyramids into tetrahedra. This process is called {\it
stellation}. Stellating all the bipyramids of the decomposition obtained from
Proposition \ref{p:tori_decomp} we obtained a triangulation of the
complement of $L$ which is made up of {\it horizontal} edges (edges from the
graph of the torihedra), {\it vertical} edges (edges from coning vertices of the
the graph of the torihedra) and stellating edges.  \end{remark}

{\it Proof.}  Using the decomposition from Proposition
\ref{p:tori_decomp} we can add a stellation edge whose end points
are $T^2 \times \{-1\}$ and $T^2 \times \{1\}$ which cut through faces of $T^2
\times I$ which do not come from the augmentation disks like in \cite{CKP2}.
Since each face of the top torihedron gets glued to the bottom torihedron, we
obtain bipyramids, and the stellation edge will decompose the bipyramids into
tetrahedra. Then the link of the vertex  $T^2 \times \{1\}$ or $T^2 \times
\{-1\}$ is the graph of the torihedron $T^2 \times [0,1)$ or $T^2 \times (-1,0]$
respectively. \qed

@@

View the Euclidean plane as the boundary of the upper-half space.
Then $\Pol_f$ supports an ideal hyperbolic pyramid $P_f$.

@@

For a hyperbolic link $K$ in $T^2 \times I$, we produce sufficient conditions on augmentations such that the resulting link obtained from augmenting $K$ is hyperbolic. The idea is to start with a graph from the torihedral decomposition of the link $K$ which will give us a graph on each torihedron with $\pi/2$ edges \cite{CKP2}. Then by results of \cite{BandS} there exist a corresponding right-angled circle pattern. We then consider the augmented link $L$ and its torihedral decomposition from Proposition \ref{p:tori_decomp} with a corresponding ``degenerate" circle pattern. We deform this degenerate circle pattern into a ``proper" circle pattern which will give us a polyhedral decomposition of $(T^2 \times I)-L$ with angles of the torihedra in our torihedral decomposition. Which we can further decompose into tetrahedra with angles satisfying conditions of an angle structure.

@@

\begin{define}
A \emph{base-angled ideal pyramid}
is a pyramid whose base is an $n$-gon, $n \geq 3$,
and each boundary edge $e_i$ of the base face is assigned a dihedral angle
$\alpha_i > 0$ such that the sum is $\sum \alpha_i = 2\pi$.
The vertical edge $e_i'$ that meets $e_i$ and $e_{i+1}$
is automatically assigned the dihedral angle $\pi - \alpha_i - \alpha_{i+1}$.
\end{define}

Clearly, the dihedral angles of an ideal hyperbolic pyramid
make it a base-angled ideal pyramid
(with $\alpha_i = \vphi_{e_i}$).
(TODO probably vice-versa?)
Also, an angled ideal tetrahedron is simply a base-angled ideal pyramid
with base a triangle, and with no preferred face.

@@

\begin{proof}
Induct on $n$; there is nothing to prove for the base case $n=3$.

Suppose the edges are labelled $e_i$,
which goes between vertices $v_i$ and $v_{i+1}$,
and suppose $e_i$ is assigned dihedral angle $\alpha_i$.
Let $e'$ be a new edge addeed to the base face of $P_n$
such that it separates the base face into a triangle and
an $(n-1)$-gon;
suppose the sides of the triangle are
$e_i, e_{i+1}$, and $e'$.
The new face corresponding to $e'$ separates $P_n$ into
an ideal tetrahedron $T$ and an ideal pyramid $P_{n-1}$.
We assign the dihedral angle of $\pi - \alpha_i - \alpha_{i+1}$
to $e'$ in $T$, and assign $\alpha_i + \alpha_{i+1}$ to $e'$ in $P_{n-1}$.
Clearly the condition that the sum of dihedral angles are satisfied
in $T$ and $P_{n-1}$.
It remains to check that the dihedral angles assigned to the vertical edges
are correct.
For the vertical edge associated $v_j$ for $j \neq i, i+2$,
there is nothing to check;
for $j = i$, the dihedral angles are
$\pi - \alpha_i - (\pi - \alpha_i - \alpha_{i-1})$
in $T$ and $\pi - \alpha_{i-1} - (\alpha_i + \alpha_{i+1})$ in $P_{n-1}$,
which sum to $\pi - \alpha_i - \alpha_{i+1}$;
it is similar for $j = i+2$.

See Figure \ref{TODO}
\end{proof}

@@

\begin{define}
Given a face $f$ of the original link diagram the \emph{augmentation sequence}
of $f$, denoted $\sigma_f$, is a cyclical sequence of symbols $0, L, R$ indexed
by vertices of $f$ going counter-clockwise, where, for $v \in \partial f$, the
$v$-th element is
\[
\sigma_f^v = 
\begin{cases}
0 \text{ if $v$ is not augmented} \\
L \text{ if $v$ is left-augmented} \\
R \text{ if $v$ is right-augmented}
\end{cases}
\]
\end{define}

\begin{prop}
Suppose $L$ is obtained from augmenting $K$,
so that for each face $f$ of the link projection of $K$,
the augmentation sequence $\sigma_f$ has no $L$ adjacent to $R$.
Then the TODO CONTINUE HERE
\end{prop}

@@

\begin{proof}
By ckp [TODO look up precise thm number],
$\toruscomp{K}$ can be decomposed
into two torihedra whose graphs are the projection graph of $K$,
which we denote by $\Gamma$.
By assigning angles $\pi/2$ to each edge of the torihedra graphs,
we can invoke \cite[Theorem 3]{BandS} to give us a circle pattern
on the projection graph.

By \prpref{p:tori_decomp}, $\toruscomp{L}$ can be
obtained by gluing two torihedra with graph $\Gamma_T(L)$ and $\Gamma_B(L)$.
Recall that $\Gamma_T(L)$ is obtained from $\Gamma$ by some slight
modifications, specifically by replacing augmented vertices with bow-ties.
We assign angles to edges of the bow-ties as in TODO figure,
and leave untouched edges with the same assignment of $\pi/2$;
we do the same for $\Gamma_B(L)$.

We can think of a bow-tie in $\Gamma_T(L)$ as ``thickened edges" in the
following sense: consider the bow-tie at a crossing $v$,
and let the edges $e,e'$ of $\Gamma$ at $v$
be associated to the over-strand of $K$.
There is a cellular map from each triangle of the bow-tie
on to $e, e'$ that identifies the $\pi/2$- and 0-labelled edges,
and collapses the $\pi$-labelled edges onto $v$
(TODO see same figure).
It is not hard to see that this map extends to a cellular map
$\Psi: \Gamma_T(L) \to \Gamma$,
and in fact extends to the faces as well.
A similar story applies to $\Gamma_B$.

Now we construct an extended circle pattern for $\Gamma_T(L)$.
We will give a more precise description,
but let us first give the picture.
Under $\Psi$,
each face $f$ of $\Gamma_T(L)$ that is not in a bow-tie
is identified with a face $\bar{f}$ of $\Gamma$,
so we assign the circle of $\bar{f}$ to $f$;
each triangle face $f$ in a bow-tie is collapsed to an edge,
and we assign to $f$ the circle circumscribing the
face of $\Gamma$ that meets $f$ along the 0-labelled edge.
This is a ``degenerate" circle pattern that can be thought of as
the limit of some (singular) circle patterns.

Let us make this more precise,
describing an extended circle pattern $c$
on $\Gamma_T(L)$.
Let the circle pattern for $\Gamma$ be given by
$\bar{c} = ((r_f),(\vphi_{\vec{e}}))$,
where recall $r_f$ is the radius of the circle $C_f$
circumscribing $f$ and $\vphi_{\vec{e}}$
is half the angle subtended by the edge $e$
at the center of $C_f$.
For non-bow-tie faces $f$ of $\Gamma_T(L)$,
$\Psi$ identifies $f$ with the face $\bar{f}$ of $\Gamma$.
We set $r_f(c) = r_{\bar{f}}(\bar{c})$.
For $\vphi$ of its edges,
if $\vec{e} \in \del f$ is labelled $\pi$,
we set $\vphi_{\vec{e}} = 0$;
otherwise, $\Psi$ identifies $\vec{e}$
with the edge $\vec{e}'$ in $\Gamma$,
then we set $\vphi_{\vec{e}}(c) = \vphi_{\vec{e}'}(\bar{c})$.

For a triangular face $f$ of a bow tie,
let $\vec{e}_0, \vec{e}_{\pi/2}, \vec{e}_{\pi}$
be the edges of $f$ labelled $0,\pi/2, \pi$ respectively.
We set $r_f(c) = r_{f'}(c)$,
where $f'$ is the face adjacent to $f$ across $e_0$.
Then we set
$\vphi_{\vec{e}_{\pi/2}} = \vphi_{\cev{e}_0} = \pi - \vphi_{\vec{e}_0}$
and $\vphi_{\vec{e}_{\pi}} = 0$.

It can be easily checked that $c$ satisfies the conditions of
\prpref{p:nghd_lift}.

with the same procedure for $\Gamma_B(L)$.

Our torihedral decomposition has graph and on augmentation we will give 0 and pi angles. Next we add another edge and give blah angle (we have three cases)
do three cases with pictures

@@

TODO consistent torus symbol, consistent thickened torus symbols
